---
title: "In Class EDA Activity"
author: "Your Name"
date: '2022-10-04'
output: pdf_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read data

The data is how much graduate students with engineering degree earn.  We will talk about the origin of the data after your submission.

```{r}
RawData<- read.csv("Engineering_graduate_salary_Simple.csv")
```

Here are the description of the variables included:

- ID: A unique ID to identify a candidate
- Salary: Annual CTC offered to the candidate (in INR)
- Gender: Candidate's gender
- DOB: Date of birth of the candidate
- CollegeID: Unique ID identifying the university/college which the candidate attended for her/his undergraduate
- CollegeTier: Each college has been annotated as 1 or 2. The annotations have been computed from the average AMCAT scores obtained by the students in the college/university. Colleges with an average score above a threshold are tagged as 1 and others as 2.
- Degree: Degree obtained/pursued by the candidate
- Specialization: Specialization pursued by the candidate
- CollegeGPA: Aggregate GPA at graduation
- CollegeCityID: A unique ID to identify the city in which the college is located in.
- CollegeCityTier: The tier of the city in which the college is located in. This is annotated based on - the population of the cities.
- CollegeState: Name of the state in which the college is located
- GraduationYear: Year of graduation (Bachelor's degree)

## Clean Data

```{r}

```

## EDA

```{r}

```

