---
title: "In Class EDA Activity"
author: "Jing Xu"
date: '2022-10-04'
output: pdf_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

## Read data

The data is how much graduate students with engineering degree earn.  We will talk about the origin of the data after your submission.

```{r}
RawData<- read.csv("Engineering_graduate_salary_Simple.csv")
```

Here are the description of the variables included:

- ID: A unique ID to identify a candidate
- Salary: Annual CTC offered to the candidate (in INR)
- Gender: Candidate's gender
- DOB: Date of birth of the candidate
- CollegeID: Unique ID identifying the university/college which the candidate attended for her/his undergraduate
- CollegeTier: Each college has been annotated as 1 or 2. The annotations have been computed from the average AMCAT scores obtained by the students in the college/university. Colleges with an average score above a threshold are tagged as 1 and others as 2.
- Degree: Degree obtained/pursued by the candidate
- Specialization: Specialization pursued by the candidate
- CollegeGPA: Aggregate GPA at graduation
- CollegeCityID: A unique ID to identify the city in which the college is located in.
- CollegeCityTier: The tier of the city in which the college is located in. This is annotated based on - the population of the cities.
- CollegeState: Name of the state in which the college is located
- GraduationYear: Year of graduation (Bachelor's degree)

## Clean Data

```{r}
RawData$male <- 0
RawData$g_college <- 0
RawData$master <- 0
RawData$avegpa <- 0
RawData$salary_lg <- 0
g <- mean(RawData$collegeGPA)
for (i in RawData$X){
  if (RawData$Gender[i] =="m")
    RawData$male[i] <- 1
  if (RawData$CollegeTier[i] ==1)
    RawData$g_college[i] <- 1
  if (RawData$Degree[i] == "MCA")
    RawData$master[i] <- 1
  RawData$avegpa[i] <- RawData$collegeGPA[i] - g
  RawData$salary_lg[i] <- log(RawData$Salary[i])
}

```

## EDA


```{r}
fit_1 <- lm(salary_lg ~ g_college + avegpa, data = RawData)
summary(fit_1)
c <- coef(fit_1)
ggplot(RawData,aes(avegpa,salary_lg))+
  geom_point(data=RawData %>% filter(g_college==0), col = "red")+
  geom_point(data=RawData %>% filter(g_college==1), col = "blue"
             ) 
color <- ifelse(RawData$g_college==0,"red", "blue")
plot(RawData$avegpa,RawData$salary_lg,pch=20, col = color, xlab = 'average gpa', ylab = 'log salary')
abline(c[1], c[3],col="magenta")
abline(c[1] + c[2], c[3],col="turquoise")

#people who get their master degree is averagely earning .38% higher salary comparing to those who didn't
#1 point higher aggregate GPA at one's graduation is averagely associated with a increase of .011 percent in salary
            
  
```

